Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-31 manuscript/manuscript.Rmd
mini
readded textbox

@@

```{r}
#| label: esc-tuning-eval
#| fig.cap: "(Left panel) Tuning results for constant escapement policies: mean episode reward scatter data (averaged over 50 episodes) together with two standard deviations shaded in grey. 
#| The optimal escapement level (the one producing maximum mean harvest) is $X_{\text{esc.}}=0.62$.
#| (Middle and right panels) Reward histograms for the optimal constant escapement policy (middle) and for the DRL policy (right).
#| For both DRL and optimal constant escapement, no early episode ends are observed (i.e. all episodes last for 200 time steps)."
#| out.width: "6.5in"
#| fig.align: "center"
esc_rewards <- escapement_df |>
  group_by(escapement, rep) |>
  filter(t == max(t)) |> 
  group_by(escapement) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))

>>>>

```{r}
#| label: textbox
#| out.width: "1\\linewidth"
knitr::include_graphics("figures/textbox.png")
```

@@

```{r}
#| label: esc-tuning-eval
#| fig.cap: "(Left panel) Tuning results for constant escapement policies: mean episode reward scatter data (averaged over 50 episodes) together with two standard deviations shaded in grey. 
#| The optimal escapement level (the one producing maximum mean harvest) is $X_{\\text{esc.}}=0.62$.
#| (Middle and right panels) Reward histograms for the optimal constant escapement policy (middle) and for the DRL policy (right).
#| For both DRL and optimal constant escapement, no early episode ends are observed (i.e. all episodes last for 200 time steps)."
#| out.width: "6.5in"
#| fig.align: "center"
esc_rewards <- escapement_df |>
  group_by(escapement, rep) |>
  filter(t == max(t)) |> 
  group_by(escapement) |>
  summarise(mean_reward = mean(reward),
            sd = sd(reward))
